---
title: "Brand prediction"
author: "Joan Claverol - Data mentor"
date: "16 de marzo de 2019"
output: 
  ioslides_presentation:
    widescreen: true
    css: JB_style.css 
    smaller: true
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)


# libraries to use
if(require(pacman) == FALSE){
  install.packages("pacman")
}

pacman::p_load(knitr, kableExtra, gridExtra)
```

## Defining the problem {.smaller}

The sales team engaged a market research firm to conduct a survey of our existing customers. 

* Objective: *find out which of two brands of computers our customers prefer*. 

* Problem: the answer to the brand preference question was not properly captured for all of the respondents.

Our work in that task would be:

1. to investigate if customer responses to some survey questions (e.g. income, age, etc.) enable us to predict the answer to the brand preference question.

2. to make those predictions and provide the sales team with a complete view of what brand our customers prefer.

## Import the data {.smaller}

```{r import the data}
completed_survey <- read.csv("../data/CompleteResponses.csv")
incompleted_survey <- read.csv("../data/SurveyIncomplete.csv")
```

```{r understanding the data we have, echo=TRUE, message=F}
library(dplyr)
glimpse(completed_survey)
glimpse(incompleted_survey)
```

## Data wrangling: giving names

Let's put the brand information in a nicer way:

```{r echo=T, message=F, warning=FALSE}
# transform the survey result to names
completed_survey$brand_name <- apply(completed_survey["brand",drop=F],
                                     MARGIN = 1,
                                     function(x) if_else(x == 0, "Acer", "Sony"))
```

```{r warning=F, message=F}
kable(head(completed_survey), format = "markdown") %>%
  kable_styling(bootstrap_options = "striped", font_size = 7)
```

## Data wrangling: tranforming to factor

Now is the moment to transform the variables to factors from the incomplete survay:

```{r echo=TRUE}
categ_var <- c("elevel", "car", "zipcode", "brand_name")
completed_survey[categ_var] <- lapply(completed_survey[categ_var], as.factor)

# let's check the structure of the dataset
glimpse(completed_survey)
```

```{r warning=FALSE, echo=TRUE}
# We can apply the same process to the incomplete survey
incompleted_survey$brand_name <- apply(incompleted_survey["brand",drop=F],
                                       MARGIN = 1,
                                       function(x) if_else(x == 0, "Acer", "Sony"))
incompleted_survey[categ_var] <- lapply(incompleted_survey[categ_var], as.factor)
```

## 1st exploration

Understand the brand preference with the **complete survey**.

* Table of absolute frequency 

```{r echo=TRUE}
table(completed_survey$brand_name, dnn = c("Brand"))
```

* Table of relative frequency

```{r echo=TRUE}
round(prop.table(table(completed_survey$brand_name, dnn = c("Brand"))),2)
```

## 1st modalisation

```{r, echo=TRUE, message=FALSE}
library(caret)
set.seed(2019)

# train and test
train_ids <- createDataPartition(y = completed_survey$brand,
                                 p = 0.75,
                                 list = F)
train <- completed_survey[train_ids,]
test <- completed_survey[-train_ids,]

# cross validation
ctrl <- trainControl(method = "repeatedcv",
                     repeats = 5,
                     number = 3)

# Creating the model with caret and using the model rpart
mod_caret_dt <- caret::train(brand_name ~ .,
                             data = train %>% dplyr::select(-brand),
                             method = "rpart",
                             trControl = ctrl)
```

## 1st error check: Accuracy and kappa

### Results on train

```{r echo=TRUE}
train_results <- predict(object = mod_caret_dt, 
                         newdata = train)
postResample(train$brand_name, train_results)
```

### Results on test 

```{r echo=TRUE}
test_results <- predict(object = mod_caret_dt, 
                        newdata = test)
postResample(test$brand_name, test_results)
```

## 1st error check: variable importance

```{r fig.align="center", fig.height=4.5, message=F, warning=F}
temp <- as.data.frame(matrix(nrow = length(varImp(mod_caret_dt)$importance$Overall)))
temp$var_name <- row.names(varImp(mod_caret_dt)$importance)
temp$var_importance <- varImp(mod_caret_dt)$importance$Overall

library(ggplot2)
plot_importance <- temp %>%
  filter(var_importance > 0) %>%
  ggplot() + geom_col(aes(x = reorder(var_name, desc(-var_importance)), 
                          y = var_importance), fill = "red", width = 0.5) + 
    coord_flip() + theme_bw() + 
    labs(title = "Importance of the variables in the model",
         y = "Importance")
plot_importance + theme(axis.title.y = element_blank())
```

## 1st error check: confusion matrix

### Confusion matrix on train

```{r message=F, warning=F, echo=T}
round(prop.table(confusionMatrix(train$brand_name, train_results)$table),2)
```


### Confusion matrix on test

```{r message=F, warning=F, echo=T}
round(prop.table(confusionMatrix(test$brand_name, test_results)$table),2)
```

## 2nd exploration

Looking for the relation between the important variable and brand. **Goal** create a model that is not overfitted to the data:

```{r echo=TRUE, fig.align="center", fig.height=4, fig.width=7}
completed_survey %>% 
  ggplot(aes(age, salary)) +
    geom_point(aes(color = brand_name))
```

## 2nd modalisation

This time im only going to use **salary** and **age** to maket the predictions:

```{r}
# Creating the model with caret and using the model rpart
mod_caret_dt_subs <- caret::train(brand_name ~ salary + age,
                                  data = train %>% dplyr::select(-brand),
                                  method = "rpart",
                                  trControl = ctrl)
```

### Results on train

```{r echo=TRUE}
train_results_2ndmod <- predict(object = mod_caret_dt_subs, 
                                newdata = train)
postResample(train$brand_name, train_results_2ndmod)
```

### Results on test 

```{r echo=TRUE}
test_results_2ndmod <- predict(object = mod_caret_dt_subs, 
                               newdata = test)
postResample(test$brand_name, test_results_2ndmod)
```

## 2nd error check: confusion matrix

We are going to compare the confusion matrix for the first model (all the variables) and the model with salary and age:

### Rpart model with all the variables

```{r echo=T}

round(prop.table(confusionMatrix(test$brand_name, test_results)$table),2)
```

### Rpart model with only salary and age

```{r echo=T}
round(prop.table(confusionMatrix(test$brand_name, test_results_2ndmod)$table),2)
```

## 2nd error check: visualization of the errors

```{r fig.align="center", fig.width = 10}
test$pred1_brand_name <- test_results
test$pred2_brand_name <- test_results_2ndmod

plot1 <- test %>% 
  ggplot(aes(x = age, y = salary)) +
    geom_point(aes(color = (brand_name != pred1_brand_name))) +
    labs(title = "Rpart model error with all variables") +
    scale_color_manual(values = c("white","red")) +
    theme(legend.position="none")

plot2 <- test %>% 
  ggplot(aes(x = age, y = salary)) +
    geom_point(aes(color = (brand_name != pred2_brand_name))) +
    labs(title = "Rpart model error with only salary and age") +
    scale_color_manual(values = c("white","red")) +
    theme(legend.position="none")

library(gridExtra)
grid.arrange(plot1, plot2, nrow = 1)
```

## 3rd modalization

Creation of the model with **KNN**

```{r echo=T}
# Creating the model with caret and using the model rpart
mod_caret_knn_subs <- caret::train(brand_name ~ salary + age,
                                   data = train %>% dplyr::select(-brand),
                                   method = "knn",
                                   trControl = ctrl,
                                   preProcess = c("center","scale")) 
```

## 3rd error check: train and test metrics

### Results on train

```{r echo=TRUE}
train_results_3rdmod <- predict(object = mod_caret_knn_subs, 
                                newdata = train)
postResample(train$brand_name, train_results_3rdmod)
```

### Results on test 

```{r echo=TRUE}
test_results_3rdmod <- predict(object = mod_caret_knn_subs, 
                                 newdata = test)
postResample(test$brand_name, test_results_3rdmod)
```

## 3rd error check: confusion matrix

### rpart model with only salary and age

```{r echo=T}
round(prop.table(confusionMatrix(test$brand_name, test_results_2ndmod)$table),2)
```

### knn model with only salary and age

```{r echo=T}
round(prop.table(confusionMatrix(test$brand_name, test_results_3rdmod)$table),2)
```

## 3rd error check: visualization of the errors

```{r fig.align="center", fig.width = 10}
test$pred3_brand_name <- test_results_3rdmod

plot3 <- test %>% 
  ggplot(aes(x = age, y = salary)) +
    geom_point(aes(color = (brand_name != pred3_brand_name))) +
    labs(title = "Knn model error with only salary and age") +
    scale_color_manual(values = c("white","red")) +
    theme(legend.position="none")

library(gridExtra)
grid.arrange(plot2, plot3, nrow = 1)
```

## 4rth modalisation: trying SVM algorithm

```{r echo=T, message=F, warning=F}
library(e1071)
mod_svm <- svm(brand_name ~ salary + age, 
               data = train)
```

### Results on train 

```{r echo=TRUE}
train_results_4rthmod <- predict(object = mod_svm, 
                                newdata = train)
postResample(train$brand_name, train_results_4rthmod)
```

### Results on test 

```{r echo=TRUE}
test_results_4rthmod <- predict(object = mod_svm, 
                                newdata = test)
postResample(test$brand_name, test_results_4rthmod)
```

## 4rth error check: confusion matrix

### KNN model with only salary and age

```{r echo=T}
# rpart model with only salary and age
round(prop.table(confusionMatrix(test$brand_name, test_results_3rdmod)$table),3)
```

### SVM model with only salary and age

```{r echo=T}
# rpart model with only salary and age
round(prop.table(confusionMatrix(test$brand_name, test_results_4rthmod)$table),3)
```

## 4rth error check: error visualization

```{r fig.align="center", fig.width = 10}
test$pred4_brand_name <- test_results_4rthmod

plot4 <- test %>% 
  ggplot(aes(x = age, y = salary)) +
    geom_point(aes(color = (brand_name != pred4_brand_name))) +
    labs(title = "SVM model error with only salary and age") +
    scale_color_manual(values = c("white","red")) +
    theme(legend.position="none")

library(gridExtra)
grid.arrange(plot3, plot4, nrow = 1)
```

## Extra: support lines plot for SVM

```{r fig.align="center", fig.height=5}
plot(mod_svm, data = test, salary ~ age)
```

